---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# addAadtData 

<!-- badges: start -->
[![R-CMD-check](https://github.com/geomarker-io/addAadtData/workflows/R-CMD-check/badge.svg)](https://github.com/geomarker-io/addAadtData/actions)
<!-- badges: end -->

The goal of `addAadtData` is to add Average Annual Daily Traffic (AADT) data from the U.S. Department of Transportation [Federal Highway Administration](https://www.fhwa.dot.gov/policyinformation/hpms/shapefiles_2017.cfm) to geocoded data.

Input data should have columns called `lat` and `lon` that contain geographic coordinates. `addAadtData` estimates the exposure to traffic within a user-specified radius (defaults to 400 m) around the input coordinates. Specifically, the `length` of roads (in meters), the average daily number of vehicles multiplied by the length of the roads (`vehicle_meters`), and the average daily number of trucks multiplied by the length of the roads (`truck_meters`) are calculated. 

Each of these variables is broken down by traffic type, as defined below:

| **traffic type** |  **types of roads** | **FHA F_System Classification** |
|--------------------|-------------------|-------------------|
| `moving` | interstates, expressways, and freeways | `Interstate` and `Principal Arterial - Other Freeways and Expressways` |
| `stop_go` | arterial roads (frequent stops lights, etc) | `Principal Arterial - Other` and `Minor Arterial` |

## Installation

Because this package contains all the aadt data, it takes a few minutes to install.

``` r
# adjust options to allow for longer download
options(timeout = 300)

# install.packages("remotes")
devtools::install_github("geomarker-io/addAadtData")
```

## Example

```{r example}
library(addAadtData) 

d <- tibble::tribble(
  ~id,       ~lat,        ~lon,
  55001310120,         NA,          NA,
  55000100280,   39.19674,  -84.582601,
  55000100281,   39.28765,  -84.510173,
  55000100282,  39.158521,  -84.417572,
  55000100283,  39.158521,  -84.417572,
  55000100284, 39.2747872, -84.8203868,
  55000100285, 39.2810336, -84.8564059,
)

add_aadt(d)
```
